Supplementary Materials

### 2023-07-06 manuscript/supplementary.tex
ms changes

\subsection{Demographic Expansion and Recessive Simulation Tests}

\begin{figure}[htbp]
    \label{suppfig:sim-exp}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/supplementary/subfigure_sim_mle_expansion.pdf}
  \caption{}
\end{figure}

\begin{figure}[htbp]
  \label{suppfig:sim-rec}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/supplementary/subfigure_sim_mle_recessive.pdf}
  \caption{}
\end{figure}

@@

@@

\subsection{Chromosome Fit Figures}

>>>>

\subsection{Demographic Expansion and Recessive Simulation Tests}
\label{supp:sim-assum}

\begin{figure}[htbp]
    \label{suppfig:sim-exp}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/supplementary/subfigure_sim_mle_expansion.pdf}

  \caption{Simulations to diagnose the effect of population exponential
      expansion on our composite likelihood estimates. The simulated population
      expansion occurs at a rate of 0.4\% a generation, starting $9.3N$ (out of
      $10N$) generations in. These parameters were meant to approximate the
  European expansion parameters estimated by \textcite{Gutenkunst2009-pg}.
Overall, we see little impact on estimated parameters.}

\begin{figure}[htbp]
  \label{suppfig:sim-rec}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/supplementary/subfigure_sim_mle_recessive.pdf}

  \caption{Simulations to diagnose the effect of non-additive mutations. These
      simulations use a dominance coefficient of $h=0.3$, i.e. the selective
      effects are $1$ ancestral state, $1+hs$ for heterozygotes, and $1+s$ for
      homozygotes. We find that slightly recessive mutations have little effect
      on the estimated selection coefficient when selection is strong,
      consistent with the fact that only the selective effect in heterozygotes
      matters when mutations are kept at low frequency by strong selection.
      However, our B' method underestimates weak selection coefficients when
      mutation effects are recessive. This is because recessive mutations are
      removed far more efficiently once they reach appreciable frequencies and
      are found in heterozygotes. Since our theory assumes additive effects, it
      accommodates by estimating weaker selection coefficients.}

@@

\subsection{Spatial Residuals}
\label{supp:spatial-residuals}

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.8\textwidth]{figures/supplementary/spatial_residual.pdf}
  \label{suppfig:spatial-residuals}
\end{figure}

@@

\subsection{Chromosome Fit Figures}
\label{supp:chrom-fit}
